---
title: "CARNIVAL on A549 and CALU-3 cell lines after SARS-CoV-2 infection"
author: "Alberto Valdeolivas: alberto.valdeolivas@bioquant.uni-heidelberg.de; Date:"
date: "27/08/2020"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### License Info

This program is free software: you can redistribute it and/or modify it under 
the terms of the GNU General Public License as published by the Free Software 
Foundation, either version 3 of the License, or (at your option) any later 
version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY 
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR 
A PARTICULAR PURPOSE. See the GNU General Public License for more details.

Please check http://www.gnu.org/licenses/.

## Introduction

The present script takes pathway and tf activity on A549 and CALU-3
cell lines after SARS-CoV-2 infection and runs CARNIVAL

### Getting Ready 

We first load the required libraries and we define a function to export CARNIVAL
results to Cytoscape and another one to extract CARNIVAL results. 

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(OmnipathR)
library(CARNIVAL)
library(gprofiler2)
library(plotly)

OutputCyto <- function(CarnivalResults, outputFile) {
    CarnivalNetwork <- 
        as.data.frame(CarnivalResults$weightedSIF, stringsAsFactors = FALSE) %>%
        dplyr::mutate(Sign = as.numeric(Sign), Weight = as.numeric(Weight)) %>% 
        dplyr::mutate(Weight = Sign * Weight) %>%
        dplyr::select(Node1, Weight, Node2)
        
    CarnivalNetworkNodes <- 
        unique(c(CarnivalNetwork$Node1,CarnivalNetwork$Node2))
    
    CarnivalAttributes <- CarnivalResults$nodesAttributes %>% 
        as.data.frame() %>%
        dplyr::filter(Node %in% CarnivalNetworkNodes) %>%
        dplyr::mutate(NodeType = as.character(NodeType)) %>%
        dplyr::mutate(NodeType=if_else(NodeType =="", "I", NodeType))
            
    nameOutputNetwork <- paste0(outputFile, "Network.sif")
    nameOutputAttributes <-  paste0(outputFile, "Attributes.txt")    
    
    write.table(CarnivalNetwork, file = nameOutputNetwork,
        quote = FALSE, row.names = FALSE, col.names = FALSE, sep = " ")
    
    write.table(CarnivalAttributes, file = nameOutputAttributes,
        quote = FALSE, row.names = FALSE, col.names = TRUE, sep = "\t")
}

extractCARNIVALnodes <- function(CarnivalResults){

    CarnivalNetwork <- 
        as.data.frame(CarnivalResults$weightedSIF, stringsAsFactors = FALSE)
    
    colnames(CarnivalNetwork) <- c("source", "sign", "target", "Weight")

    ## We define the set of nodes interesting for our condition
    sucesses <- unique(c(gsub("_.*","",CarnivalNetwork$source), 
        gsub("_.*","",CarnivalNetwork$target)))

    CarnivalAttributes <- as.data.frame(CarnivalResults$nodesAttributes, 
        stringsAsFactors = FALSE)

    ## We define the background as all the genes in our prior knowledge network.
    bg <- unique(gsub("_.*","",CarnivalAttributes$Node))     
    
    return(list(sucesses = sucesses, bg= bg))
}
```

### Generating the prior knowledge network from Omnipath

```{r pkn1, eval=FALSE}
### Prior knowledge network from Omnipath. 
ia_omnipath <- import_omnipath_interactions() %>% as_tibble()
ia_pwextra <- import_pathwayextra_interactions() %>% as_tibble()
ia_kinaseextra <- import_kinaseextra_interactions() %>% as_tibble()

## We bind the datasets
interactions <- as_tibble(
  bind_rows(
    ia_omnipath %>% mutate(type = 'ppi'),
    ia_pwextra %>% mutate(type = 'ppi'),
    ia_kinaseextra %>% mutate(type = 'ppi')))

signed_directed_interactions <- 
  dplyr::filter(interactions, consensus_direction==1) %>%
  filter(consensus_stimulation == 1 | consensus_inhibition == 1) %>% 
  dplyr::mutate(sign = if_else(consensus_stimulation==1,1,-1))  %>%
  dplyr::select(source_genesymbol, sign,  target_genesymbol) %>%
  dplyr::rename(source ="source_genesymbol", target ="target_genesymbol")

carnival_pkn <- signed_directed_interactions %>%
  dplyr::distinct(source, target, .keep_all = TRUE)
saveRDS(carnival_pkn, file="Intermediate_FIles/carnival_pkn.rds")
```

```{r pkn2}
carnival_pkn<- readRDS("Intermediate_FIles/carnival_pkn.rds")
all_source_nodes <- unique(carnival_pkn$source)
all_target_nodes <- unique(carnival_pkn$target)
all_nodes_network <- unique(c(all_source_nodes,all_target_nodes))
```

### Reading TF and pathway activity and perturbed nodes. 

```{r inputs, message=FALSE, warning=FALSE}
### Dorothea + Progeny Results 
dorothea_results <- 
  read_csv(file = "CARNIVAL_input/virus_signatures_dorothea.csv") %>% 
  dplyr::rename(Tf = "X1")

progeny_results <- 
  read_csv(file = "CARNIVAL_input/virus_signatures_progeny.csv") %>% 
  dplyr::rename(Pathway = "X1")

### Perturbation nodes
perturbations_nodes <- 
  read_csv(file = "CARNIVAL_input/virus_signatures_pert.csv") %>% 
  dplyr::select(Gene, Mechanism)
```

## Results

### Early phase: RIG-I-Like receptors as perturbation

For the early response to SARS-CoV-2 infection, we set the RIG-I-Like receptors
as perturbed. 

```{r RIG_receptors}
RIG_perturbation <- perturbations_nodes %>%
  dplyr::filter(Mechanism == "RIG") %>% 
  dplyr::mutate(sign = 1) %>% 
  dplyr::select(Gene, sign) %>% 
  tibble::column_to_rownames(var = "Gene") %>%
  t() %>% as.data.frame()
```

We also check if these nodes are present in our prior knowledge network as 
source of interactions (otherwise it does not make sense to include its 
perturbation). 

```{r RIG_check}
colnames(RIG_perturbation) 
colnames(RIG_perturbation) %in% all_source_nodes
```

#### GSE147507.S5_A549_SARS.CoV.2

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE147507_A549}
dorothea_results_GSE147507_A549 <- dorothea_results %>% 
  dplyr::select(Tf, GSE147507.S5_A549_SARS.CoV.2) %>% 
  dplyr::filter(Tf %in% all_nodes_network) %>%
  dplyr::top_n(25, wt = abs(GSE147507.S5_A549_SARS.CoV.2)) %>%
  dplyr::arrange(GSE147507.S5_A549_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE147507_A549 <- progeny_results %>% 
  dplyr::select(Pathway,GSE147507.S5_A549_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE147507_A549, eval=FALSE}
carnival_results_GSE147507_A549 <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE147507_A549,
    inputObj = RIG_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE147507_A549,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE147507_A549, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549.rds")
OutputCyto(carnival_results_GSE147507_A549, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549")
```

We now run the enrichment analysis: 

```{r enrichment_GSE147507_A549}
carnival_results_GSE147507_A549 <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549.rds")
nodes_carnival_GSE147507_A549 <- 
  extractCARNIVALnodes(carnival_results_GSE147507_A549)

enrichment_results_GSE147507_A549 <- 
  gost(nodes_carnival_GSE147507_A549$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE147507_A549$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE147507_A549, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE147507_A549, capped = FALSE, interactive = TRUE)
```


#### GSE147507.S7_Calu3_SARS.CoV.2

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE147507_CALU3}
dorothea_results_GSE147507_CALU3 <- dorothea_results %>% 
  dplyr::select(Tf, GSE147507.S7_Calu3_SARS.CoV.2) %>% 
  dplyr::filter(Tf %in% all_nodes_network) %>%
  dplyr::top_n(25, wt = abs(GSE147507.S7_Calu3_SARS.CoV.2)) %>%
  dplyr::arrange(GSE147507.S7_Calu3_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE147507_CALU3 <- progeny_results %>% 
  dplyr::select(Pathway,GSE147507.S7_Calu3_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE147507_CALU3, eval=FALSE}
carnival_results_GSE147507_CALU3 <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE147507_CALU3,
    inputObj = RIG_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE147507_CALU3,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE147507_CALU3, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3.rds")
OutputCyto(carnival_results_GSE147507_CALU3, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3")
```

We now run the enrichment analysis: 

```{r enrichment_GSE147507_CALU3}
carnival_results_GSE147507_CALU3 <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3.rds")
nodes_carnival_GSE147507_CALU3 <- 
  extractCARNIVALnodes(carnival_results_GSE147507_CALU3)

enrichment_results_GSE147507_CALU3 <- 
  gost(nodes_carnival_GSE147507_CALU3$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE147507_CALU3$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE147507_CALU3, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE147507_CALU3, capped = FALSE, interactive = TRUE)
```

#### GSE148729_Calu3_SARS.CoV.2_24H

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE148729_CALU3}
dorothea_results_GSE148729_CALU3 <- dorothea_results %>% 
  dplyr::select(Tf, GSE148729_Calu3_SARS.CoV.2_24H) %>% 
  dplyr::top_n(25, wt = abs(GSE148729_Calu3_SARS.CoV.2_24H)) %>%
  dplyr::arrange(GSE148729_Calu3_SARS.CoV.2_24H) %>%
  dplyr::filter(Tf %in% all_nodes_network) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE148729_CALU3 <- progeny_results %>% 
  dplyr::select(Pathway,GSE148729_Calu3_SARS.CoV.2_24H) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE148729_CALU3, eval=FALSE}
carnival_results_GSE148729_CALU3 <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE148729_CALU3,
    inputObj = RIG_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE148729_CALU3,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE148729_CALU3, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3.rds")
OutputCyto(carnival_results_GSE148729_CALU3, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3")
```

We now run the enrichment analysis: 

```{r enrichment_GSE148729_CALU3}
carnival_results_GSE148729_CALU3 <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3.rds")
nodes_carnival_GSE148729_CALU3 <- 
  extractCARNIVALnodes(carnival_results_GSE148729_CALU3)

enrichment_results_GSE148729_CALU3 <- 
  gost(nodes_carnival_GSE148729_CALU3$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE148729_CALU3$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE148729_CALU3, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE148729_CALU3, capped = FALSE, interactive = TRUE)
```

### Later phase: RIG-I-Like and interferon receptors as perturbation

For a later response to SARS-CoV-2 infection, we set the RIG-I-Like and the 
interferon receptors as perturbed. 

```{r RIG_IFN_receptors}
RIG_IFN_perturbation <- perturbations_nodes %>%
  dplyr::filter(Mechanism %in% c("RIG","IFN")) %>% 
  dplyr::mutate(sign = 1) %>% 
  dplyr::select(Gene, sign) %>% 
  tibble::column_to_rownames(var = "Gene") %>%
  t() %>% as.data.frame()
```

We also check if these nodes are present in our prior knowledge network as 
source of interactions (otherwise it does not make sense to include its 
perturbation). 

```{r RIG_IFN_check}
colnames(RIG_IFN_perturbation) 
colnames(RIG_IFN_perturbation) %in% all_source_nodes
```

#### GSE147507.S5_A549_SARS.CoV.2

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE147507_A549_IFN}
dorothea_results_GSE147507_A549 <- dorothea_results %>% 
  dplyr::select(Tf, GSE147507.S5_A549_SARS.CoV.2) %>% 
  dplyr::filter(Tf %in% all_nodes_network) %>%
  dplyr::top_n(25, wt = abs(GSE147507.S5_A549_SARS.CoV.2)) %>%
  dplyr::arrange(GSE147507.S5_A549_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE147507_A549 <- progeny_results %>% 
  dplyr::select(Pathway,GSE147507.S5_A549_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE147507_A549_IFN, eval=FALSE}
carnival_results_GSE147507_A549_IFN <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE147507_A549,
    inputObj = RIG_IFN_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE147507_A549,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE147507_A549_IFN, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549_IFN.rds")
OutputCyto(carnival_results_GSE147507_A549_IFN, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549_IFN")
```

We now run the enrichment analysis: 

```{r enrichment_GSE147507_A549_IFN}
carnival_results_GSE147507_A549_IFN <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE147507_A549_IFN.rds")
nodes_carnival_GSE147507_A549_IFN <- 
  extractCARNIVALnodes(carnival_results_GSE147507_A549_IFN)

enrichment_results_GSE147507_A549_IFN <- 
  gost(nodes_carnival_GSE147507_A549_IFN$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE147507_A549_IFN$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE147507_A549_IFN, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE147507_A549_IFN, capped = FALSE, interactive = TRUE)
```

#### GSE147507.S7_Calu3_SARS.CoV.2

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE147507_CALU3_IFN}
dorothea_results_GSE147507_CALU3 <- dorothea_results %>% 
  dplyr::select(Tf, GSE147507.S7_Calu3_SARS.CoV.2) %>% 
  dplyr::filter(Tf %in% all_nodes_network) %>%
  dplyr::top_n(25, wt = abs(GSE147507.S7_Calu3_SARS.CoV.2)) %>%
  dplyr::arrange(GSE147507.S7_Calu3_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE147507_CALU3 <- progeny_results %>% 
  dplyr::select(Pathway,GSE147507.S7_Calu3_SARS.CoV.2) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE147507_CALU3_IFN, eval=FALSE}
carnival_results_GSE147507_CALU3_IFN <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE147507_CALU3,
    inputObj = RIG_IFN_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE147507_CALU3,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE147507_CALU3_IFN, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3_IFN.rds")
OutputCyto(carnival_results_GSE147507_CALU3_IFN, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3_IFN")
```

We now run the enrichment analysis: 

```{r enrichment_GSE147507_CALU3_IFN}
carnival_results_GSE147507_CALU3_IFN <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE147507_CALU3_IFN.rds")
nodes_carnival_GSE147507_CALU3_IFN <- 
  extractCARNIVALnodes(carnival_results_GSE147507_CALU3_IFN)

enrichment_results_GSE147507_CALU3_IFN <- 
  gost(nodes_carnival_GSE147507_CALU3_IFN$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE147507_CALU3_IFN$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE147507_CALU3_IFN, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE147507_CALU3_IFN, capped = FALSE, interactive = TRUE)
```

#### GSE148729_Calu3_SARS.CoV.2_24H

We select this condition and prepared the inputs to run CARNIVAL

```{r CARNIVAL_input_GSE148729_CALU3_IFN}
dorothea_results_GSE148729_CALU3 <- dorothea_results %>% 
  dplyr::select(Tf, GSE148729_Calu3_SARS.CoV.2_24H) %>% 
  dplyr::top_n(25, wt = abs(GSE148729_Calu3_SARS.CoV.2_24H)) %>%
  dplyr::arrange(GSE148729_Calu3_SARS.CoV.2_24H) %>%
  dplyr::filter(Tf %in% all_nodes_network) %>%
  tibble::column_to_rownames(var = "Tf")  %>%
  t() %>% as.data.frame()

progeny_results_GSE148729_CALU3 <- progeny_results %>% 
  dplyr::select(Pathway,GSE148729_Calu3_SARS.CoV.2_24H) %>%
  tibble::column_to_rownames(var = "Pathway")  %>%
  t()
```

And we finally run CARNIVAL:

```{r carnival_GSE148729_CALU3_IFN, eval=FALSE}
carnival_results_GSE148729_CALU3_IFN <-runCARNIVAL(
    solverPath="/home/alvaldeolias/Downloads/cplex",
    netObj=carnival_pkn,
    measObj=dorothea_results_GSE148729_CALU3,
    inputObj = RIG_IFN_perturbation,
    # dir_name="Carnival_Results",
    weightObj=progeny_results_GSE148729_CALU3,
    # nodeID = 'gene',
    timelimit = 7200,
    solver = "cplex")
saveRDS(carnival_results_GSE148729_CALU3_IFN, 
    file = "CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3_IFN.rds")
OutputCyto(carnival_results_GSE148729_CALU3_IFN, 
    outputFile="CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3_IFN")
```

We now run the enrichment analysis: 

```{r enrichment_GSE148729_CALU3_IFN}
carnival_results_GSE148729_CALU3_IFN <- 
    readRDS("CARNIVAL_results/viral_signatures/carnival_results_GSE148729_CALU3_IFN.rds")
nodes_carnival_GSE148729_CALU3_IFN <- 
  extractCARNIVALnodes(carnival_results_GSE148729_CALU3_IFN)

enrichment_results_GSE148729_CALU3_IFN <- 
  gost(nodes_carnival_GSE148729_CALU3_IFN$sucesses, user_threshold = 0.01, 
  correction_method = "gSCS", custom_bg = nodes_carnival_GSE148729_CALU3_IFN$bg,
  sources = c("KEGG","REAC","WP","GO:BP","MIRNA")) 
```

```{r plot_GSE148729_CALU3_IFN, dpi=300, out.height= 700, out.width=800, warning=FALSE, echo=TRUE}
gostplot(enrichment_results_GSE148729_CALU3_IFN, capped = FALSE, interactive = TRUE)
```


## Session Info Details

```{r, echo=FALSE, eval=TRUE}
sessionInfo()
```
