---
title: "Comparing CARNIVAL output: Viral VS Drug Signatures"
author: "Alberto Valdeolivas: alberto.valdeolivas@bioquant.uni-heidelberg.de; Date:"
date: "07/09/2020"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### License Info

This program is free software: you can redistribute it and/or modify it under 
the terms of the GNU General Public License as published by the Free Software 
Foundation, either version 3 of the License, or (at your option) any later 
version.

This program is distributed in the hope that it will be useful, but WITHOUT ANY 
WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR 
A PARTICULAR PURPOSE. See the GNU General Public License for more details.

Please check http://www.gnu.org/licenses/.

## Introduction

The present script takes the CARNIVAL outputs generated from viral (SARS-CoV-2 
infection) and drug signatures with anti-viral effect and compare them. 

### Getting Ready 

We first load the required libraries. 

```{r libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(gprofiler2)
library(plotly)
library(ggplot2)
```

## Results 

To first explore the similarity between CARNIVAL results on viral signatures
and drug signatures, we are going to compute the Jaccard index for the shared nodes and interactions in the output networks for every condition. 

```{r}
path_drug <-"CARNIVAL_results/drug_signatures/"
path_virus <- "CARNIVAL_results/viral_signatures/"

files_viral_signatures <- 
  list.files(path = path_virus, pattern = "\\.rds$")
files_drug_signatures <- 
  list.files(path= path_drug, pattern = "\\.rds$")

len_viral <- length(files_viral_signatures)
len_drugs <- length(files_drug_signatures)
len_df <- len_viral* len_drugs

results_df <- 
  data.frame(
    viral_cell = character(length = len_df), 
    drug = character(length = len_df), 
    jaccard_nodes = numeric(length = len_df),
    jaccard_interactions = numeric(length = len_df),
    common_nodes = character(length = len_df),
    common_interactions = character(length = len_df))

a <- 1

for (i in seq_along(files_drug_signatures)){
  current_drug <- 
    str_replace(str_replace(files_drug_signatures[i], 
    "carnival_results_", ""), ".rds","")
  curent_file_drug <- readRDS(paste0(path_drug,files_drug_signatures[i]))
  current_network_drug <- curent_file_drug$weightedSIF %>% 
    as_data_frame()
  current_nodes_drug <- current_network_drug %>% 
    dplyr::pull(Node1, Node2) %>% 
    unique()
  for (j in seq_along(files_viral_signatures)){
    current_celldataset <- 
      str_replace(str_replace(files_viral_signatures[j], 
      "carnival_results_", ""), ".rds","")
    curent_file_virus <- readRDS(paste0(path_virus,files_viral_signatures[j]))
    current_network_virus <- curent_file_virus$weightedSIF %>% 
      as_data_frame()
    current_nodes_virus <- current_network_virus %>% 
      dplyr::pull(Node1, Node2) %>% 
      unique()
    common_nodes <- intersect(current_nodes_drug, current_nodes_virus)
    common_interactions <- 
      dplyr::inner_join(current_network_drug, current_network_virus, 
        by = c("Node1", "Sign", "Node2"))
    jaccard_nodes <- length(common_nodes)/ 
      (length(current_nodes_virus) + length(current_nodes_drug))
    jaccard_interactions <- nrow(common_interactions)/
      (nrow(current_network_drug) + nrow(current_network_virus))
    results_df$viral_cell[a] <- current_celldataset
    results_df$drug[a] <- current_drug
    results_df$jaccard_nodes[a] <- jaccard_nodes
    results_df$jaccard_interactions[a] <- jaccard_interactions
    results_df$common_nodes[a] <- paste0(common_nodes, collapse = " ; ")
    results_df$common_interactions[a] <- common_interactions %>% 
      dplyr::mutate(inter = paste0(Node1, "  ", Sign, "  ", Node2)) %>% 
      dplyr::pull(inter) %>% paste0(collapse = " ; ")
    a <- a + 1
  }
}
```

### Jaccard Index at the node level

Then, we plot the results at the node level

```{r}
sim_nodes <- 
  ggplot(results_df, aes(viral_cell, drug)) +
  geom_tile(aes(fill=jaccard_nodes), colour = "white") +
  scale_fill_gradient(low = "#b7f7ff", high = "#0092a3") + 
  theme_minimal() + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_text(size = 8,
        angle = 90))
```

```{r,dpi=300,echo=FALSE,fig.height=10, fig.width=10}
sim_nodes
```

### Jaccard Index at the interaction level

And then at the interaction level. 

```{r}
sim_interactions <- 
  ggplot(results_df, aes(viral_cell, drug)) +
  geom_tile(aes(fill=jaccard_interactions), colour = "white") +
  scale_fill_gradient(low = "#b7f7ff", high = "#0092a3") + 
  theme_minimal() + 
  theme(axis.ticks = element_blank(),
        axis.text.x = element_text(size = 8,
        angle = 90))
```

```{r,dpi=300,echo=FALSE,fig.height=10, fig.width=10}
sim_interactions
```

## Session Info Details

```{r, echo=FALSE, eval=TRUE}
sessionInfo()
``````
